\documentclass[12pt]{article}
\pagestyle{empty} 
\renewcommand*\rmdefault{ppl}
\linespread{1.6}
\usepackage[margin=1in]{geometry}
\usepackage[parfill]{parskip}
\begin{document}

\emph{First}, take this piece of paper, and tear it in half
where the line crosses it. Hand the bottom half to your buddy.

\emph{Then}, you (and your buddy's) task during this section is to
read a bug report against a real project. You'll each explain it to
each other after you're done understanding it. If you are not sure
what is going on, feel free to ask your buddy for help.

Remember that this is a real bug in a real project!

Nickname: "No December"

Link: https://code.google.com/p/android/issues/detail?id=39692

Questions you should be able to answer (OK if you can't answer all):

\begin{itemize}
\item What is the problem the person is experiencing?
\item On what date did the wrong behavior get introduced?
\item Who is the person who fixed the behavior?
\end{itemize}

\hrulefill

You (and your buddy's) task during this section is to read a bug
report against a real project. You'll each explain it to each other
after you're done understanding it. If you are not sure what is going
on, feel free to ask your buddy for help.

Remember that this is a real bug in a real project!

Nickname: "Can't print... sometimes"

Link: https://bugs.launchpad.net/ubuntu/+source/cupsys/+bug/255161

Questions you should be able to answer:

\begin{itemize}
\item Are there particular days of the week that people can reliably print?
\item Does uninstalling OpenOffice.org and reinstalling it help fix the problem?
\item What is the actual cause of the problem?
\end{itemize}

\end{document}
